---
title: <b> "Comparing perfomance FDK and TTQuoteHistoryClient " </b>
author: 
date: '`r Sys.time()`'
output: html_document
params:
  symbol: EURUSD
--- 
  
  
```{r setup, cache = F, echo = F, message = F, warning = F, tidy = F, results='hide'}
DeleteLastElements <-function(table)
{
  if(nrow(table)>1)
    {
      while(TRUE)
      {
        buf <- tail(table$DateTime,n=2)
        if(buf[1]==buf[2])
        {
          table <- head(table,n = -1)
        }
        else
        {
          break
        }
      }
  }
  return(table)
}

if(!require("data.table")){ 
  install.packages("data.table", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(data.table) 
} 
if(!require("plyr")){ 
  install.packages("plyr", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(plyr) 
} 

if(!require("compare")){ 
  install.packages("compare", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(compare) 
} 

if(!require("DT")){ 
 install.packages("DT", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
 library(DT) 
} 

if(!require("plotly")){ 
 install.packages("plotly", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
 library(plotly) 
 } 


# ##########################vars#################################
TickDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,07,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,07,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,12,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,05,12,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,29,3,00,00)), as.POSIXct(0,origin=ISOdatetime(2017,01,29,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,02,29,3,00,00)))

#TickDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)))

TickDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,07,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,07,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,12,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,05,12,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,29,3,00,00)), as.POSIXct(0,origin=ISOdatetime(2017,01,29,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,02,29,3,00,00)))


#BarDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,05,3,00,00)))

startTimeTicks<-as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00))
endTimeTicks <- as.POSIXct(0,origin=ISOdatetime(2017,01,03,20,00,00))
startTimeBars<- as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00))
endTimeBars <- as.POSIXct(0,origin=ISOdatetime(2017,01,05,3,00,00))
symbol <- "EURUSD"
resultTableTime <-data.table()
resultTableSpeed<-data.table()
resultTickTable <-data.table()
resultTickL2Table <- data.table()
resultBarTable <- data.table()
countTicks = 0
countL2 = 0
countBars_bid = 0
time_ticks_fdk <- 0
time_ticks_cache <- 0
time_ticksL2_fdk <- 0
time_ticksL2_cache <- 0
time_bars_ask_fdk <- 0
time_bars_ask_cache <- 0
time_bars_bid_fdk <- 0
time_bars_bid_cache <- 0
step = 604800
iterTime = startTimeTicks
TTSAddress = "tpdemo.fxopen.com"
TTSLogin = "59932"
TTSPassword = "8mEx7zZ2"

tz <- "UTC" 
utits = "secs" 


require(rFdk)
require(rTTQuoteHistory)

ttConnect(TTSAddress,TTSLogin,TTSPassword)
tthConnect(TTSAddress,TTSLogin,TTSPassword)
while(iterTime < endTimeTicks)
{
  if (iterTime + step > endTimeTicks)
  {
    step <- endTimeTicks - iterTime
  }
  
  #########################  TiCKS     ###############################
  
  
  st <- Sys.time()
  ticks_fdk <-
  ttFeed.TickBestHistory(symbol, iterTime, iterTime + step)
  et <- Sys.time()
  time_taken <- difftime(et, st, tz, utits)
  time_ticks_fdk <- round(time_ticks_fdk + time_taken, 2)
  
  countTicks <- as.integer(countTicks + nrow(ticks_fdk))
  count <- nrow(ticks_fdk)
  if (count < 1000)
  {
    st <- Sys.time()
    ticks_cache <- tthTickRequest(symbol, iterTime + step, count)
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticks_cache <- round(time_ticks_cache + time_taken, 2)
  }
  else
  {
    st <- Sys.time()
    ticks_cache <- tthTickRequest(symbol, iterTime,-1000)
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticks_cache <- time_ticks_cache + time_taken
    ticks_cache <- DeleteLastElements(ticks_cache)
    cache_count <- nrow(ticks_cache)
    while (cache_count < count - 1000)
    {
      st <- Sys.time()
      ticks_cache <-
      tthTickRequest(symbol, tail(ticks_cache$DateTime, n = 1),-1000)
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_ticks_cache <- time_ticks_cache + time_taken
      ticks_cache <- DeleteLastElements(ticks_cache)
      cache_count <- cache_count + nrow(ticks_cache)
    }
    st <- Sys.time()
    ticks_cache <-tthTickRequest(symbol,tail(ticks_cache$DateTime, n = 1),-(count - cache_count))
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticks_cache <- round(time_ticks_cache + time_taken, 2)
  }
  #   #######################    L2     #################################
  
  
  
  st <- Sys.time()
  ticksL2_fdk <-
  ttFeed.TickLevel2History(symbol, iterTime, iterTime + step, 5)
  et <- Sys.time()
  time_taken <- difftime(et, st, tz, utits)
  time_ticksL2_fdk <- round(time_ticksL2_fdk + time_taken, 2)
  
  countL2 <- as.integer(countL2 + floor(nrow(ticksL2_fdk) / 5))
  count <- as.integer(floor(nrow(ticksL2_fdk) / 5))
  if (count < 1000)
  {
    st <- Sys.time()
    ticksL2_cache <- tthTickL2Request(symbol, iterTime,-count)
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticksL2_cache <-
    round(time_ticksL2_cache + time_taken, 2)
  }
  else
  {
    st <- Sys.time()
    ticksL2_cache <- tthTickL2Request(symbol, iterTime,-1000)
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticksL2_cache <- time_ticksL2_cache + time_taken
    ticksL2_cache <- DeleteLastElements(ticksL2_cache)
    cache_count <- as.integer(floor(nrow(ticksL2_cache) / 5))
    while (cache_count < count - 1000)
    {
      st <- Sys.time()
      ticksL2_cache <-
      tthTickL2Request(symbol, tail(ticksL2_cache$DateTime, n = 1),-1000)
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_ticksL2_cache <- time_ticksL2_cache + time_taken
      ticksL2_cache <- DeleteLastElements(ticksL2_cache)
      cache_count <-
      as.integer(floor(nrow(ticksL2_cache) / 5)) + cache_count
    }
    st <- Sys.time()
    ticksL2_cache <-
    tthTickL2Request(symbol,
    tail(ticksL2_cache$DateTime, n = 1),
    -(count - cache_count))
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticksL2_cache <-
    round(time_ticksL2_cache + time_taken, 2)
  }
  iterTime <- iterTime + step
}


step = 604800
iterTime = startTimeBars
while(iterTime<endTimeBars)
{
  if(iterTime + step > endTimeBars)
  {
    step <- endTimeBars - iterTime
  }
#   ##########################    Bars_Bid    ##############################

 
  
  st <- Sys.time()
  bars_bid_fdk <- ttFeed.BarHistory(symbol,"Bid",startTime = iterTime,endTime = (iterTime + step))
  et <- Sys.time()
  time_taken <- difftime(et, st, tz, utits)
  time_bars_bid_fdk <- round(time_bars_bid_fdk + time_taken,2)

  countBars_bid <- as.integer(countBars_bid + nrow(bars_bid_fdk))
  count <- nrow(bars_bid_fdk)

  if(count < 1000)
  {
    st <- Sys.time()
    bars_bid_cache <- tthBarRequest(symbol,iterTime, -count,priceType = "Bid")
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_bars_bid_cache <- round(time_bars_bid_cache + time_taken,2)
  }
  else
  {
    st <- Sys.time()
    bars_bid_cache <- tthBarRequest(symbol,iterTime, -1000,priceType = "Bid")
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_bars_bid_cache <-time_bars_bid_cache + time_taken
    cache_count <- 1000
    while(cache_count < count - 1000)
    {
      st <- Sys.time()
      bars_bid_cache <- tthBarRequest(symbol,tail(bars_bid_cache$DateTime,n=1), -1000,priceType = "Bid")
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_bars_bid_cache <-time_bars_bid_cache + time_taken

      cache_count <- cache_count + 1000
    }
    st <- Sys.time()
    bars_bid_cache <- tthBarRequest(symbol,tail(bars_bid_cache$DateTime,n=1), -(count - cache_count),priceType = "Bid")
    et <- Sys.time()
    time_bars_bid_cache <- round(time_bars_bid_cache + et - st,2)
  }
  ########################################################
  
#  st <- Sys.time()
#  bars_ask_fdk <- ttFeed.BarHistory(symbol,"Ask",startTime = startTime,endTime = endTime)
#  et <- Sys.time()
#  time_bars_ask_fdk <- round(time_bars_ask_fdk+et - st,2)
#
#  count <- nrow(bars_ask_fdk)
  
#  if(count < 1000)
#  {
#    st <- Sys.time()
#    bars_ask_cache <- tthBarRequest(symbol,endTime, count,priceType = "Ask")
#    et <- Sys.time()
#    time_bars_ask_cache <-time_bars_ask_cache+ et - st
#  }
#  else
#  {
#    st <- Sys.time()
#    bars_ask_cache <- tthBarRequest(symbol,endTime, 1000,priceType = "Ask")
#    et <- Sys.time()
#    time_bars_ask_cache <-time_bars_ask_cache+ et - st
#    cache_count <- 1000
#    while(cache_count < count - 1000)
#    {
#      st <- Sys.time()
#      bars_ask_cache <- tthBarRequest(symbol,tail(bars_ask_cache$DateTime,n=1), -1000,priceType = "Ask")
#      et <- Sys.time()
#      time_bars_ask_cache <- time_bars_ask_cache+et - st
#
#      cache_count <- cache_count + 1000
#    }
#    st <- Sys.time()
#    bars_ask_cache <- tthBarRequest(symbol,tail(bars_ask_cache$DateTime,n=1), -(count - cache_count),priceType = "Ask")
#    et <- Sys.time()
#    time_bars_ask_cache <- round(time_bars_ask_cache+et - st,2)
#  }
  iterTime <- iterTime + step
  cat("\014")
}




 resultTableTime <- rbind(resultTableTime, data.table(names=c("rFDK", "rTTQuoteHistory"),  "TimeTicks, sec"=c(time_ticks_fdk,time_ticks_cache), "TimeL2, sec"=    c(time_ticksL2_fdk,time_ticksL2_cache), "TimeBars_bid, sec"= c(time_bars_bid_fdk,time_bars_bid_cache)))
 
 speed_ticks_fdk = round(countTicks/as.numeric(time_ticks_fdk),0)
 speed_ticks_cache = round(countTicks/as.numeric(time_ticks_cache),0)
 
 speed_l2_fdk = round(countL2/as.numeric(time_ticksL2_fdk),0)
 speed_l2_cache = round(countL2/as.numeric(time_ticksL2_cache),0)
   
 speed_bars_bid_fdk = round(countBars_bid/as.numeric(time_bars_bid_fdk),0)
 speed_bars_bid_cache = round(countBars_bid/as.numeric(time_bars_bid_cache),0)
 
 resultTableSpeed <- rbind(resultTableSpeed, data.table(names=c("rFDK", "rTTQuoteHistory"), "Ticks per sec"=c(speed_ticks_fdk,speed_ticks_cache), "L2 per sec"= c(speed_l2_fdk,speed_l2_cache),  "Bars per sec"= c(speed_bars_bid_fdk,speed_bars_bid_cache)))


```

<b> Plan: </b> <br>
  1) FDK: Getting ticks from TT Server  <br>
  2) Cash: FDK: Getting ticks from TT Server  <br>
  3) FDK: Getting L2 from TT Server  <br>
  4) Cash: FDK: Getting L2 from TT Server  <br>
  5) FDK: Getting bars from TT Server  <br>
  6) Cash: FDK: Getting bars from TT Server  <br>
 
 <br>
  
  TT Server name:  <b>  `r  TTSAddress ` </b>   <br> 
  Count ticks:  <b>  `r  countTicks ` </b>   <br> 
  Ticks period: from `r startTimeTicks ` to `r endTimeTicks ` <br> 
  <br>
  Count bars:  <b>  `r  countBars_bid ` </b>   <br> 
  Bars period: from `r startTimeBars ` to `r endTimeBars ` <br> 
  
 <h3>Time table </h3>
```{r echo=F}
datatable(resultTableTime)
```

 <h3> Speed table </h3>
```{r echo=F}
datatable(resultTableSpeed)
```


<br>

```{r cache = F, echo = F, message = F, warning = F, tidy = F}

for(i in 1:(length(TickDateArray)/2))
{
  countTicks = 0
  countL2 = 0
  time_ticks_fdk <- 0
  time_ticks_cache <- 0
  time_ticksL2_fdk <- 0
  time_ticksL2_cache <- 0
  step = 604800
  iterTime = TickDateArray[2*i-1]
  while(iterTime<TickDateArray[2*i])
  {
    if(iterTime + step > TickDateArray[2*i])
    {
      step <- TickDateArray[2*i] - iterTime
    }
  
    #########################  TiCKS     ###############################
  
    
    st <- Sys.time()
    ticks_fdk <- ttFeed.TickBestHistory(symbol,iterTime,iterTime + step)
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_ticks_fdk <- round(time_ticks_fdk + time_taken,2)
  
    countTicks <- as.integer(countTicks + nrow(ticks_fdk))
    count <- nrow(ticks_fdk)
    if(count<1000)
    {
      st <- Sys.time()
      ticks_cache <- tthTickRequest(symbol,iterTime + step, count)
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_ticks_cache <- round(time_ticks_cache + time_taken,2)
    }
    else
    {
      st <- Sys.time()
      ticks_cache <- tthTickRequest(symbol,iterTime, -1000)
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_ticks_cache <- time_ticks_cache + time_taken
      ticks_cache <- DeleteLastElements(ticks_cache)
      cache_count <- nrow(ticks_cache)
      while(cache_count < count - 1000)
      {
        st <- Sys.time()
        ticks_cache <- tthTickRequest(symbol,tail(ticks_cache$DateTime,n=1), -1000)
        et <- Sys.time()
        time_taken <- difftime(et, st, tz, utits)
        time_ticks_cache <- time_ticks_cache + time_taken
        ticks_cache <- DeleteLastElements(ticks_cache)
        cache_count <- cache_count + nrow(ticks_cache)
      }
      st <- Sys.time()
      ticks_cache <- tthTickRequest(symbol,tail(ticks_cache$DateTime,n=1), -(count - cache_count))
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_ticks_cache <- round(time_ticks_cache + time_taken,2)
    }
  #   #######################    L2     #################################
  
  
    
    st <- Sys.time()
     ticksL2_fdk <- ttFeed.TickLevel2History(symbol,iterTime,iterTime + step,5)
     et <- Sys.time()
     time_taken <- difftime(et, st, tz, utits)
     time_ticksL2_fdk <- round(time_ticksL2_fdk + time_taken,2)
     
     countL2 <- as.integer(countL2 + floor(nrow(ticksL2_fdk)/5))
     count <- as.integer(floor(nrow(ticksL2_fdk)/5))
     if(count<1000)
     {
       st <- Sys.time()
       ticksL2_cache <- tthTickL2Request(symbol,iterTime, -count)
     et <- Sys.time()
     time_taken <- difftime(et, st, tz, utits)
       time_ticksL2_cache <- round(time_ticksL2_cache + time_taken,2)
     }
     else
     {
       st <- Sys.time()
       ticksL2_cache <- tthTickL2Request(symbol,iterTime, -1000)
       et <- Sys.time()
       time_taken <- difftime(et, st, tz, utits)
       time_ticksL2_cache <- time_ticksL2_cache + time_taken
       ticksL2_cache <- DeleteLastElements(ticksL2_cache)
       cache_count <- as.integer(floor(nrow(ticksL2_cache)/5))
       while(cache_count < count - 1000)
       {
         st <- Sys.time()
         ticksL2_cache <- tthTickL2Request(symbol,tail(ticksL2_cache$DateTime,n=1), -1000)
         et <- Sys.time()
         time_taken <- difftime(et, st, tz, utits)
         time_ticksL2_cache <- time_ticksL2_cache + time_taken 
         ticksL2_cache <- DeleteLastElements(ticksL2_cache)
         cache_count <- as.integer(floor(nrow(ticksL2_cache)/5)) + cache_count
       }
       st <- Sys.time()
       ticksL2_cache <- tthTickL2Request(symbol,tail(ticksL2_cache$DateTime,n=1), -(count - cache_count))
       et <- Sys.time()
       time_taken <- difftime(et, st, tz, utits)
       time_ticksL2_cache <- round(time_ticksL2_cache + time_taken,2)
     }
     iterTime <- iterTime + step
  }
  resultTickTable <- rbind(resultTickTable,data.table(count = countTicks, timeTickFDK = time_ticks_fdk, timeTickTTH = time_ticks_cache))
  resultTickL2Table <-rbind(resultTickL2Table,data.table(countL2 = countL2, timeL2FDK = time_ticksL2_fdk, timeL2TTH = time_ticksL2_cache))
}

for(i in 1:(length(BarDateArray)/2))
{
  countBars_bid = 0
  countBars_ask = 0
  time_bars_ask_fdk <- 0
  time_bars_ask_cache <- 0
  time_bars_bid_fdk <- 0
  time_bars_bid_cache <- 0
  step = 604800
  iterTime = BarDateArray[2*i-1]
  while(iterTime<BarDateArray[2*i])
  {
  if(iterTime + step > BarDateArray[2*i])
  {
    step <- BarDateArray[2*i] - iterTime
  }
#   ##########################    Bars_Bid    ##############################

 
  
  st <- Sys.time()
  bars_bid_fdk <- ttFeed.BarHistory(symbol,"Bid",startTime = iterTime,endTime = (iterTime + step))
  et <- Sys.time()
  time_taken <- difftime(et, st, tz, utits)
  time_bars_bid_fdk <- round(time_bars_bid_fdk + time_taken,2)

  countBars_bid <- as.integer(countBars_bid + nrow(bars_bid_fdk))
  count <- nrow(bars_bid_fdk)

  if(count < 1000)
  {
    st <- Sys.time()
    bars_bid_cache <- tthBarRequest(symbol,iterTime, -count,priceType = "Bid")
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_bars_bid_cache <- round(time_bars_bid_cache + time_taken,2)
  }
  else
  {
    st <- Sys.time()
    bars_bid_cache <- tthBarRequest(symbol,iterTime, -1000,priceType = "Bid")
    et <- Sys.time()
    time_taken <- difftime(et, st, tz, utits)
    time_bars_bid_cache <-time_bars_bid_cache + time_taken
    cache_count <- 1000
    while(cache_count < count - 1000)
    {
      st <- Sys.time()
      bars_bid_cache <- tthBarRequest(symbol,tail(bars_bid_cache$DateTime,n=1), -1000,priceType = "Bid")
      et <- Sys.time()
      time_taken <- difftime(et, st, tz, utits)
      time_bars_bid_cache <-time_bars_bid_cache + time_taken

      cache_count <- cache_count + 1000
    }
    st <- Sys.time()
    bars_bid_cache <- tthBarRequest(symbol,tail(bars_bid_cache$DateTime,n=1), -(count - cache_count),priceType = "Bid")
    et <- Sys.time()
    time_bars_bid_cache <- round(time_bars_bid_cache + et - st,2)
  }
  ########################################################
  
#  st <- Sys.time()
#  bars_ask_fdk <- ttFeed.BarHistory(symbol,"Ask",startTime = startTime,endTime = endTime)
#  et <- Sys.time()
#  time_bars_ask_fdk <- round(time_bars_ask_fdk+et - st,2)
#
#  count <- nrow(bars_ask_fdk)
  
#  if(count < 1000)
#  {
#    st <- Sys.time()
#    bars_ask_cache <- tthBarRequest(symbol,endTime, count,priceType = "Ask")
#    et <- Sys.time()
#    time_bars_ask_cache <-time_bars_ask_cache+ et - st
#  }
#  else
#  {
#    st <- Sys.time()
#    bars_ask_cache <- tthBarRequest(symbol,endTime, 1000,priceType = "Ask")
#    et <- Sys.time()
#    time_bars_ask_cache <-time_bars_ask_cache+ et - st
#    cache_count <- 1000
#    while(cache_count < count - 1000)
#    {
#      st <- Sys.time()
#      bars_ask_cache <- tthBarRequest(symbol,tail(bars_ask_cache$DateTime,n=1), -1000,priceType = "Ask")
#      et <- Sys.time()
#      time_bars_ask_cache <- time_bars_ask_cache+et - st
#
#      cache_count <- cache_count + 1000
#    }
#    st <- Sys.time()
#    bars_ask_cache <- tthBarRequest(symbol,tail(bars_ask_cache$DateTime,n=1), -(count - cache_count),priceType = "Ask")
#    et <- Sys.time()
#    time_bars_ask_cache <- round(time_bars_ask_cache+et - st,2)
#  }
  iterTime <- iterTime + step
  cat("\014")
}
  resultBarTable <- rbind(resultBarTable,data.table(count = countBars_bid, timeBarFDK = time_bars_bid_fdk,timeBarTTH = time_bars_bid_cache))
}


ttDisconnect()
tthDisconnect()
```
<br>

```{r cache = F, echo = F, message = F, warning = F, tidy = F}

plot_ly(resultTickTable, x = resultTickTable$count) %>%
    add_trace(y = resultTickTable$timeTickFDK, name = 'rFDK', mode = 'lines') %>%
    add_trace(y = resultTickTable$timeTickTTH, name = 'TTQuoteHistoryClient', mode = 'lines') %>%
    layout(title = "Chart downloading Ticks",
         xaxis = list(title = "Count Ticks"),
         yaxis = list (title = "Time downloading, sec"))

```
<br>

```{r cache = F, echo = F, message = F, warning = F, tidy = F}
#datatable(resultBarTable)
plot_ly(resultTickL2Table, x = resultTickL2Table$countL2) %>%
  
  add_trace(y = resultTickL2Table$timeL2FDK, name = 'rFDK',mode = 'lines') %>%
  add_trace(y = resultTickL2Table$timeL2TTH, name = 'TTQuoteHistoryClient',mode = 'lines') %>%
  layout(title = "Chart downloading L2",
         xaxis = list(title = "Count L2"),
         yaxis = list (title = "Time downloading, sec"))

```
<br>

```{r cache = F, echo = F, message = F, warning = F, tidy = F}

plot_ly(resultBarTable, x = resultBarTable$count) %>%
  
  add_trace(y = resultBarTable$timeBarFDK, name = 'rFDK',mode = 'lines') %>%
  add_trace(y = resultBarTable$timeBarTTH, name = 'TTQuoteHistoryClient',mode = 'lines') %>%
  layout(title = "Chart downloading Bars",
         xaxis = list(title = "Count Bars"),
         yaxis = list (title = "Time downloading, sec"))


```

