---
title: <b> "Comparing perfomance FDK and TTQuoteHistoryClient " </b>
author: 
date: '`r Sys.time()`'
output: html_document
params:
  symbol: EURUSD
--- 
  
  
```{r setup, cache = F, echo = F, message = F, warning = F, tidy = F, results='hide'}
if(!require("doParallel")){ 
  install.packages("doParallel", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(doParallel) 
} 
if(!require("data.table")){ 
  install.packages("data.table", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(data.table) 
} 
if(!require("plyr")){ 
  install.packages("plyr", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(plyr) 
} 

if(!require("compare")){ 
  install.packages("compare", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(compare) 
} 

if(!require("DT")){ 
  install.packages("DT", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(DT) 
} 

if(!require("plotly")){ 
  install.packages("plotly", repos = "http://cran.us.r-project.org", dependencies = TRUE)  
  library(plotly) 
} 


#TickDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,12,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,12,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,04,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,04,05,00,00)))


#BarDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,04,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,06,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,06,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,10,3,00,00)))


# ##########################vars#################################
TickDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,02,08,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,09,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,03,45,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,05,30,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,05,30,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,07,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,09,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,10,40,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,10,40,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,11,40,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,11,40,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,13,15,00)))

#TickDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)))

BarDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,19,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,17,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,07,00,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,10,17,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,19,14,00,00)), as.POSIXct(0,origin=ISOdatetime(2017,01,20,04,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,02,21,11,00,00)), as.POSIXct(0,origin=ISOdatetime(2017,02,21,11,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,05,01,03,00,00)),as.POSIXct(0,origin=ISOdatetime(2016,01,01,03,00,00)),as.POSIXct(0,origin=ISOdatetime(2016,04,29,03,00,00)))


#BarDateArray = c(as.POSIXct(0,origin=ISOdatetime(2017,01,01,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00)),as.POSIXct(0,origin=ISOdatetime(2017,01,05,3,00,00)))



IterationTick <-function(startTime,endTime)
{
  cl <- makeCluster(detectCores())
  registerDoParallel(cl)
  step = 604800
  iterTime = startTime
  while(iterTime < endTime)
  {
    if (iterTime + step > endTime)
    {
      step <- endTime - iterTime
    }
    
    #########################  TiCKS     ###############################
    for(i in 1:length(symbol))
    {
      time_taken <- system.time(ticks_fdk <-
                                  ttFeed.TickBestHistory(symbol[i], iterTime, iterTime + step))
      time_ticks_fdk <<- time_ticks_fdk + as.numeric(time_taken[3])
      
      countTicks <<- as.integer(countTicks + nrow(ticks_fdk))
      count_fdk[i] <- nrow(ticks_fdk)
    }
    time_taken1 <- system.time(time_array<-foreach(i = 1:length(symbol),.packages = "rTTQuoteHistory",.export = c("count_fdk","TTSAddress","TTSLogin","TTSPassword","symbol")) %dopar%
    {
      time_taken<-system.time(tthConnect(TTSAddress,name = paste("client",as.character(i),sep="_"),login = TTSLogin,password = TTSPassword))
      result<-time_taken[3]
      ticks_cache <-tthTickRequest(symbol[i], iterTime, -count_fdk[i])
      time_taken<-system.time(tthDisconnect())
      result<-as.numeric(time_taken[3]) + result
      result
    })
    time_ticks_cache <<- time_taken1[3] - min(unlist(time_array))
    #   #######################    L2     #################################
    for(i in 1:length(symbol))
    {
      time_taken <- system.time(ticksL2_fdk <-
                                  ttFeed.TickLevel2History(symbol[i], iterTime, iterTime + step, 5))
      time_ticksL2_fdk <<- time_ticksL2_fdk + as.numeric(time_taken[3])
      
      countL2 <<- as.integer(countL2 + floor(nrow(ticksL2_fdk) / 5))
      count_fdk[i] <<- as.integer(floor(nrow(ticksL2_fdk) / 5))
    }
    time_taken1<-system.time(time_array<-foreach(i = 1:length(symbol),.packages = "rTTQuoteHistory",.export = c("count_fdk","TTSAddress","TTSLogin","TTSPassword","symbol")) %dopar%
    {
      time_taken<-system.time(tthConnect(TTSAddress,name = paste("client",as.character(i),sep="_"),login = TTSLogin,password = TTSPassword))
      result<-time_taken[3]
      ticksL2_cache <-tthTickL2Request(symbol[i], iterTime, -count_fdk[i])
      time_taken<-system.time(tthDisconnect())
      result<-as.numeric(time_taken[3]) + result
      result
    })
    time_ticksL2_cache <<- time_taken1[3] - min(unlist(time_array))
    iterTime <- iterTime + step
  }
  stopCluster(cl)
}

IterationBar <-function(startTime,endTime)
{
  cl <- makeCluster(length(symbol))
  registerDoParallel(cl)
  step = 604800
  iterTime = startTime
  while(iterTime<endTime)
  {
    if(iterTime + step > endTime)
    {
      step <- endTime - iterTime
    }
    #   ##########################    Bars_Bid    ##############################
    for(i in 1:length(symbol))
    {
      time_taken <- system.time(bars_bid_fdk <- ttFeed.BarHistory(symbol[i],"Bid",startTime = iterTime,endTime = (iterTime + step)))
      time_bars_bid_fdk <<- time_bars_bid_fdk + as.numeric(time_taken[3])
      countBars_bid <<- as.integer(countBars_bid + nrow(bars_bid_fdk))
      count_fdk[i] <<- nrow(bars_bid_fdk)
    }
    time_taken1<-system.time(time_array<-foreach(i = 1:length(symbol),.packages = "rTTQuoteHistory",.export = c("count_fdk","TTSAddress","TTSLogin","TTSPassword","symbol")) %dopar%
    {
      time_taken<-system.time(tthConnect(TTSAddress,name = paste("client",as.character(i),sep="_"),login = TTSLogin,password = TTSPassword))
      result<-time_taken[3]
      bars_bid_cache <- tthBarRequest(symbol[i],iterTime, -count_fdk[i],priceType = "Bid")
      time_taken = system.time(tthDisconnect())
      result<-as.numeric(time_taken[3]) + result
      result
    })
    time_bars_bid_cache<<- time_taken1[3] - min(unlist(time_array))
    iterTime <- iterTime + step
  }
  stopCluster(cl)
}

startTimeTicks<-as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00))
endTimeTicks <- as.POSIXct(0,origin=ISOdatetime(2017,01,03,3,00,00))
startTimeBars<- as.POSIXct(0,origin=ISOdatetime(2017,01,02,3,00,00))
endTimeBars <- as.POSIXct(0,origin=ISOdatetime(2017,01,05,3,00,00))
symbolArray <- list(c("EURUSD"),c("NZDUSD","USDCHF"),c("GBPUSD","AUDUSD","AUDCAD"),c("USDJPY","AUDCHF","USDCAD","AUDJPY"))
resultTableTime <-data.table()
resultTableSpeed<-data.table()
resultTickTable1 <-data.table()
resultTickL2Table1 <- data.table()
resultBarTable1 <- data.table()
resultTickTable2 <-data.table()
resultTickL2Table2 <- data.table()
resultBarTable2 <- data.table()
resultTickTable3 <-data.table()
resultTickL2Table3 <- data.table()
resultBarTable3 <- data.table()
resultTickTable4 <-data.table()
resultTickL2Table4 <- data.table()
resultBarTable4 <- data.table()
resTicksAll <- data.table()

resultTickTable5 <-data.table()
resultTickL2Table5 <- data.table()
resultBarTable5 <- data.table()

resL2All <-  data.table()
resBarsAll <-  data.table()
countTicks = 0
countL2 = 0

time_taken = 0
countBars_bid = 0
time_ticks_fdk <- 0
time_ticks_cache <- 0
time_ticksL2_fdk <- 0
time_ticksL2_cache <- 0
time_bars_ask_fdk <- 0
time_bars_ask_cache <- 0
time_bars_bid_fdk <- 0
time_bars_bid_cache <- 0
ticksL2_cache = 0
ticksL2_fdk= 0
ticks_cache= 0
ticks_fdk= 0
bars_bid_cache = 0
bars_bid_fdk = 0
TTSAddress = "tp.dev.soft-fx.eu"
TTSLogin = "5"
TTSPassword = "123qwe!" 

tz <- "UTC" 
utits = "secs" 


require(rFdk)
require(rTTQuoteHistory)

ttConnect(TTSAddress,TTSLogin,TTSPassword)
symbol <-symbolArray[[1]]
count_fdk = 1:length(symbol)
for(i in 1:(length(TickDateArray)/2))
  {
    countTicks = 0
    countL2 = 0
    time_ticks_fdk <- 0
    time_ticks_cache <- 0
    time_ticksL2_fdk <- 0
    time_ticksL2_cache <- 0
    IterationTick(TickDateArray[2*i-1],TickDateArray[2*i])
    resultTickTable1 <- rbind(resultTickTable1,data.table(count = countTicks, speedTickFDK = countTicks/time_ticks_fdk, speedTickTTH = countTicks/time_ticks_cache, CountSymbols = "1"))
    
    resultTickL2Table1 <-rbind(resultTickL2Table1,data.table(countL2 = countL2, speedL2FDK  = countL2/time_ticksL2_fdk, speedL2TTH =  countL2/time_ticksL2_cache, CountSymbols = "1"))
   
  }
  resTicksAll <- rbind(resTicksAll, resultTickTable1)
  resL2All <- rbind(resL2All, resultTickL2Table1)
  
  
  for(i in 1:(length(BarDateArray)/2))
  {
    countBars_bid = 0
    countBars_ask = 0
    time_bars_ask_fdk <- 0
    time_bars_ask_cache <- 0
    time_bars_bid_fdk <- 0
    time_bars_bid_cache <- 0
    IterationBar(BarDateArray[2*i-1],BarDateArray[2*i])
    resultBarTable1 <- rbind(resultBarTable1,data.table(count = countBars_bid, speedBarFDK = countBars_bid/time_bars_bid_fdk,speedBarTTH = countBars_bid/time_bars_bid_cache, CountSymbols = "1"))
  
  }
  
  resBarsAll <- rbind(resBarsAll, resultBarTable1)
  
symbol <-symbolArray[[2]]
count_fdk = 1:length(symbol)
for(i in 1:(length(TickDateArray)/2))
  {
    countTicks = 0
    countL2 = 0
    time_ticks_fdk <- 0
    time_ticks_cache <- 0
    time_ticksL2_fdk <- 0
    time_ticksL2_cache <- 0
    IterationTick(TickDateArray[2*i-1],TickDateArray[2*i])
    resultTickTable2 <- rbind(resultTickTable2,data.table(count = countTicks, speedTickFDK = countTicks/time_ticks_fdk, speedTickTTH = countTicks/time_ticks_cache, CountSymbols = "2"))
    
    resultTickL2Table2 <-rbind(resultTickL2Table2,data.table(countL2 = countL2, speedL2FDK  = countL2/time_ticksL2_fdk, speedL2TTH =  countL2/time_ticksL2_cache, CountSymbols = "2"))
   
  }
  
resTicksAll <- rbind(resTicksAll, resultTickTable2)
resL2All <- rbind(resL2All, resultTickL2Table2)

  for(i in 1:(length(BarDateArray)/2))
  {
    countBars_bid = 0
    countBars_ask = 0
    time_bars_ask_fdk <- 0
    time_bars_ask_cache <- 0
    time_bars_bid_fdk <- 0
    time_bars_bid_cache <- 0
    IterationBar(BarDateArray[2*i-1],BarDateArray[2*i])
    resultBarTable2 <- rbind(resultBarTable2,data.table(count = countBars_bid, speedBarFDK = countBars_bid/time_bars_bid_fdk,speedBarTTH = countBars_bid/time_bars_bid_cache, CountSymbols = "2"))
  }
resBarsAll <- rbind(resBarsAll, resultBarTable2)


symbol <-symbolArray[[3]]
count_fdk = 1:length(symbol)
for(i in 1:(length(TickDateArray)/2))
  {
    countTicks = 0
    countL2 = 0
    time_ticks_fdk <- 0
    time_ticks_cache <- 0
    time_ticksL2_fdk <- 0
    time_ticksL2_cache <- 0
    IterationTick(TickDateArray[2*i-1],TickDateArray[2*i])
    resultTickTable3 <- rbind(resultTickTable3,data.table(count = countTicks, speedTickFDK = countTicks/time_ticks_fdk, speedTickTTH = countTicks/time_ticks_cache, CountSymbols = "3"))
     
    resultTickL2Table3 <-rbind(resultTickL2Table3,data.table(countL2 = countL2, speedL2FDK  = countL2/time_ticksL2_fdk, speedL2TTH =  countL2/time_ticksL2_cache, CountSymbols = "3"))
    
}

resTicksAll <- rbind(resTicksAll, resultTickTable3)
resL2All <- rbind(resL2All, resultTickL2Table3)
  
  for(i in 1:(length(BarDateArray)/2))
  {
    countBars_bid = 0
    countBars_ask = 0
    time_bars_ask_fdk <- 0
    time_bars_ask_cache <- 0
    time_bars_bid_fdk <- 0
    time_bars_bid_cache <- 0
    IterationBar(BarDateArray[2*i-1],BarDateArray[2*i])
    resultBarTable3 <- rbind(resultBarTable3,data.table(count = countBars_bid, speedBarFDK = countBars_bid/time_bars_bid_fdk,speedBarTTH = countBars_bid/time_bars_bid_cache, CountSymbols = "3"))
  }
resBarsAll <- rbind(resBarsAll, resultBarTable3)


symbol <-symbolArray[[4]]
count_fdk = 1:length(symbol)
for(i in 1:(length(TickDateArray)/2))
  {
    countTicks = 0
    countL2 = 0
    time_ticks_fdk <- 0
    time_ticks_cache <- 0
    time_ticksL2_fdk <- 0
    time_ticksL2_cache <- 0
    IterationTick(TickDateArray[2*i-1],TickDateArray[2*i])
    resultTickTable4 <- rbind(resultTickTable4,data.table(count = countTicks, speedTickFDK = countTicks/time_ticks_fdk, speedTickTTH = countTicks/time_ticks_cache, CountSymbols = "4"))
    
    resultTickTable5 <- rbind(resultTickTable5,data.table(count = countTicks, speedTickTTH = countTicks/time_ticks_fdk, speedTickFDK = countTicks/time_ticks_cache, CountSymbols = "5"))
    
    resultTickL2Table4 <-rbind(resultTickL2Table4,data.table(countL2 = countL2, speedL2FDK  = countL2/time_ticksL2_fdk, speedL2TTH =  countL2/time_ticksL2_cache, CountSymbols = "4"))
     resultTickL2Table5 <-rbind(resultTickL2Table5,data.table(countL2 = countL2, speedL2TTH  = countL2/time_ticksL2_fdk, speedL2FDK =  countL2/time_ticksL2_cache, CountSymbols = "5"))
    
  }
  
resTicksAll <- rbind(resTicksAll, resultTickTable4)
resTicksAll <- rbind(resTicksAll, resultTickTable5)

resL2All <- rbind(resL2All, resultTickL2Table4)
resL2All <- rbind(resL2All, resultTickL2Table5)

  for(i in 1:(length(BarDateArray)/2))
  {
    countBars_bid = 0
    countBars_ask = 0
    time_bars_ask_fdk <- 0
    time_bars_ask_cache <- 0
    time_bars_bid_fdk <- 0
    time_bars_bid_cache <- 0
    IterationBar(BarDateArray[2*i-1],BarDateArray[2*i])
    resultBarTable4 <- rbind(resultBarTable4,data.table(count = countBars_bid, speedBarFDK = countBars_bid/time_bars_bid_fdk,speedBarTTH = countBars_bid/time_bars_bid_cache, CountSymbols = "4"))
     resultBarTable5 <- rbind(resultBarTable5,data.table(count = countBars_bid, speedBarTTH = countBars_bid/time_bars_bid_fdk,speedBarFDK = countBars_bid/time_bars_bid_cache, CountSymbols = "5"))
  }
resBarsAll <- rbind(resBarsAll, resultBarTable4)
resBarsAll <- rbind(resBarsAll, resultBarTable5)

ttDisconnect()

```

<b> Plan: </b> <br>
  1) FDK: Getting ticks from TT Server  <br>
  2) Cash: FDK: Getting ticks from TT Server  <br>
  3) FDK: Getting L2 from TT Server  <br>
  4) Cash: FDK: Getting L2 from TT Server  <br>
  5) FDK: Getting bars from TT Server  <br>
  6) Cash: FDK: Getting bars from TT Server  <br>
 
 <br>
  
  TT Server name:  <b>  `r  TTSAddress ` </b>   <br> 
  Count ticks:  <b>  `r  countTicks ` </b>   <br> 
  Ticks period: from `r startTimeTicks ` to `r endTimeTicks ` <br> 
  <br>
  Count bars:  <b>  `r  countBars_bid ` </b>   <br> 
  Bars period: from `r startTimeBars ` to `r endTimeBars ` <br> 
  
  Ticks
 ```{r echo=F, warning = F}

p2 <- ggplot(resTicksAll, aes(x=count, y=speedTickTTH, colour=CountSymbols)) +
    geom_point(alpha=.3) +
    geom_smooth(alpha=.2, size=1) +
    ggtitle("Ticks")
p2
#plot_ly(p2)


p3 <- ggplot(resL2All, aes(x=countL2, y=speedL2TTH, colour=CountSymbols)) +
    geom_point(alpha=.3) +
    geom_smooth(alpha=.2, size=1) +
    ggtitle("L2")
p3

#plot_ly(p3)


p4 <- ggplot(resBarsAll, aes(x=count, y=speedBarTTH, colour=CountSymbols)) +
    geom_point(alpha=.3) +
    geom_smooth(alpha=.2, size=1) +
    ggtitle("Bars")
p4
    
#plot_ly(p4)
```

